Subsegmental language detection in Celtic language text

### 2014-06-28 codeswitch-cltw-2014/codeswitch_camera_ready.tex
cc4 licence
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55049 72bbbca6-d526-0410-a7d9-f06f51895060

The remainder of the paper is laid out as follows. In section~\ref{sec:method} we describe the problem
in more detail and look at relevant prior work before proposing a novel method of sub-sentential
language detection. Section~\ref{sec:eval} describes the evaluation methodology. Then in section~\ref{sec:results}
we present the results of our method and compare it against several other possible methods. Finally, section~\ref{sec:conclusions}
presents future work and conclusions.

@@

\blfootnote{
    %
    % for review submission
    %
    \hspace{-0.65cm}  % space normally used by the marker
    Place licence statement here for the camera-ready version, see
    Section~\ref{licence} of the instructions for preparing a
    manuscript.
    %
    % % final paper: en-uk version (to license, a licence)
    %
    % \hspace{-0.65cm}  % space normally used by the marker
    % This work is licensed under a Creative Commons 
    % Attribution 4.0 International Licence.
    % Page numbers and proceedings footer are added by
    % the organisers.
    % Licence details:
    % \url{http://creativecommons.org/licenses/by/4.0/}
    % 
    % % final paper: en-us version (to licence, a license)
    %
    % \hspace{-0.65cm}  % space normally used by the marker
    % This work is licenced under a Creative Commons 
    % Attribution 4.0 International License.
    % Page numbers and proceedings footer are added by
    % the organizers.
    % License details:
    % \url{http://creativecommons.org/licenses/by/4.0/}
}

>>>>

The remainder of the paper is laid out as follows. In section~\ref{sec:method} we describe the problem
in more detail and look at relevant prior work before proposing a novel method of sub-sentential
language detection. Section~\ref{sec:eval} describes the evaluation methodology. Then in section~\ref{sec:results}
we present the results of our method and compare it against several other possible methods. Finally, section~\ref{sec:conclusions}
presents future work and conclusions.
\blfootnote{
    %
    % for review submission
    %
    %\hspace{-0.65cm}  % space normally used by the marker
    %Place licence statement here for the camera-ready version, see
    %Section~\ref{licence} of the instructions for preparing a
    %manuscript.
    %
     % final paper: en-uk version (to license, a licence)

     \hspace{-0.65cm}  % space normally used by the marker
     This work is licensed under a Creative Commons 
     Attribution 4.0 International Licence.
     Page numbers and proceedings footer are added by
     the organisers.
     Licence details:
     \url{http://creativecommons.org/licenses/by/4.0/}

    % % final paper: en-us version (to licence, a license)
    %
    % \hspace{-0.65cm}  % space normally used by the marker
    % This work is licenced under a Creative Commons 
    % Attribution 4.0 International License.
    % Page numbers and proceedings footer are added by
    % the organizers.
    % License details:
    % \url{http://creativecommons.org/licenses/by/4.0/}
}

@@
